---
title: "Flexdashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
```

```{r}
csv_data <- read_csv("csv-thesaurus-matching/test_filter_Quelles_stratégies_et_secteurs_de_croissance_pour_les_sociétés_d_ingénierie_Numérique_2_20170412-114612.csv")
clean_csv_data <- csv_data %>%
  filter(interest_lvl >= 0) %>%
  mutate(interest_lvl = as.factor(interest_lvl), nb_list_matched = list_1 + list_2 + list_3, total_lists = 3, list_1 = as.logical(list_1), list_2 = as.logical(list_2), list_3 = as.logical(list_3))
```

Numérique 2
=========================================

Column {.sidebar}
-----------------------------------------------------------------------

```{r}
radioButtons("nb_matched", label = "Select number of thesaurus to be matched", choiceValues = 1:(ncol(csv_data) - 2),
             choiceNames = paste(1:(ncol(csv_data) - 2), "thesaurus out of", (ncol(csv_data) - 2)), selected = 1)
```


Row
-----------------------------------------------------------------------
### Articles retrieved

```{r}
renderValueBox(
  valueBox(nrow(csv_data), icon = "fa-comments")
)
```


### Matched articles

```{r}
matched_articles <- reactive(clean_csv_data %>%
                             filter(nb_list_matched >= input$nb_matched))
renderValueBox(
  valueBox(nrow(matched_articles()), icon = "fa-comments")
)
```

### Matched articles ratio

```{r}
matched_ratio <- reactive(round(100*nrow(matched_articles())/nrow(csv_data)))
renderGauge(
  gauge(matched_ratio(), min = 0, max = 100, symbol = "%", gaugeSectors(
    succes = c(80, 100), warning = c(31, 79), danger = c(0, 30)
  ))
)
```

Row 
-----------------------------------------------------------------------
### Articles matched  

```{r}
articles_matched <- reactive(clean_csv_data %>%
                               filter(nb_list_matched >= input$nb_matched))
renderValueBox(
  valueBox(nrow(articles_matched()), icon = "fa-comments")
)
```

### Matched articles liked 

```{r}
matched_articles_liked <- reactive(articles_matched() %>%
                             filter(interest_lvl == 2))
renderValueBox(
  valueBox(nrow(matched_articles_liked()), icon = "fa-comments", color = "info")
)
```

### Matched articles liked ratio

```{r}
matched_liked_ratio <- reactive(round(100*nrow(matched_articles_liked())/nrow(articles_matched())))
renderGauge(
  gauge(matched_liked_ratio(), min = 0, max = 100, symbol = "%", gaugeSectors(
    success = c(51, 100), warning = c(11, 50), danger = c(0, 10)
  ))
)
```

Row 
-----------------------------------------------------------------------
### Articles liked  

```{r}
articles_liked <- clean_csv_data %>%
  filter(interest_lvl == 2)
renderValueBox(
  valueBox(nrow(articles_liked), icon = "fa-comments", color = "info")
)
```

### Liked articles lost 

```{r}
liked_article_lost <- reactive(articles_liked %>% filter(nb_list_matched < input$nb_matched))
renderValueBox(
  valueBox(nrow(liked_article_lost()), icon = "fa-comments", color = "info")
)
```

### Liked articles lost ratio 

```{r}
liked_lost_ratio <- reactive(round(100*nrow(liked_article_lost())/nrow(articles_liked)))
renderGauge(
  gauge(liked_lost_ratio(), min = 0, max = 100, symbol = "%", gaugeSectors(
    danger = c(51, 100), warning = c(11, 50), succes = c(0, 10)
  ))
)
```

Row 
-----------------------------------------------------------------------

```{r}
renderPlot(
  ggplot(clean_csv_data %>%
           filter(nb_list_matched >= input$nb_matched), aes(x = interest_lvl, fill = interest_lvl)) + geom_bar() + theme_bw() +
    theme(legend.position = "none") + ylab(NULL) + xlab("Niveau d'intérêt")
)
```

Custom csv file
==================================================

Column {.sidebar}
-----------------------------------------------------------------------

```{r}
br()
fileInput("mydata", "Please load some valide csv file", accept = "csv")

custom_csv_data <- reactive({
    infile <- input$mydata
    if (is.null(infile)) {
      # User has not uploaded a file yet
      return(NULL)
    }
    read_csv(infile$datapath)
  })

```

```{r}
renderUI({
  val <- ifelse(is.null(ncol(custom_csv_data())), 1, ncol(custom_csv_data()) - 2)
  tagList(radioButtons("custom_nb_matched", label = "Select number of thesaurus to be matched", choiceValues = 1:val, choiceNames = paste("At least", 1:val, "thesaurus matched out of", val)),
          if(val>1){actionButton("go", "Analyze")})
})
```


```{r, eval=TRUE}
clean_custom_csv_data <- reactive(custom_csv_data() %>%
                                  mutate(nb_list_matched = rowSums(.[-c(1,2)])) %>%
  filter(interest_lvl >= 0) %>%
  mutate(interest_lvl = as.factor(interest_lvl))
)
```

Row
-----------------------------------------------------------------------
### Articles retrieved

```{r}
renderValueBox(
  valueBox(nrow(custom_csv_data()), icon = "fa-comments")
)
```


### Matched articles

```{r}
custom_matched_articles <- reactive(clean_custom_csv_data() %>%
                             filter(nb_list_matched >= input$custom_nb_matched))
renderValueBox(
  valueBox(nrow(custom_matched_articles()), icon = "fa-comments")
)
```

### Matched articles ratio

```{r}
custom_matched_ratio <- reactive(round(100*nrow(custom_matched_articles())/nrow(custom_csv_data())))
renderGauge(
  gauge(custom_matched_ratio(), min = 0, max = 100, symbol = "%", gaugeSectors(
    succes = c(80, 100), warning = c(31, 79), danger = c(0, 30)
  ))
)
```

Row 
-----------------------------------------------------------------------
### Articles matched  

```{r}
custom_articles_matched <- reactive(clean_custom_csv_data() %>%
                               filter(nb_list_matched >= input$custom_nb_matched))
renderValueBox(
  valueBox(nrow(custom_articles_matched()), icon = "fa-comments")
)
```

### Matched articles liked 

```{r}
custom_matched_articles_liked <- reactive(custom_articles_matched() %>%
                             filter(interest_lvl == 2))
renderValueBox(
  valueBox(nrow(custom_matched_articles_liked()), icon = "fa-comments", color = "info")
)
```

### Matched articles liked ratio

```{r}
custom_matched_liked_ratio <- reactive(round(100*nrow(custom_matched_articles_liked())/nrow(custom_articles_matched())))
renderGauge(
  gauge(custom_matched_liked_ratio(), min = 0, max = 100, symbol = "%", gaugeSectors(
    success = c(51, 100), warning = c(11, 50), danger = c(0, 10)
  ))
)
```

Row 
-----------------------------------------------------------------------
### Articles liked  

```{r}
custom_articles_liked <- reactive(clean_custom_csv_data() %>%
  filter(interest_lvl == 2))
renderValueBox(
  valueBox(nrow(custom_articles_liked()), icon = "fa-comments", color = "info")
)
```

### Liked articles lost 

```{r}
custom_liked_article_lost <- reactive(custom_articles_liked() %>% filter(nb_list_matched < input$custom_nb_matched))
renderValueBox(
  valueBox(nrow(custom_liked_article_lost()), icon = "fa-comments", color = "info")
)
```

### Liked articles lost ratio 

```{r}
custom_liked_lost_ratio <- reactive(round(100*nrow(custom_liked_article_lost())/nrow(custom_articles_liked())))
renderGauge(
  gauge(custom_liked_lost_ratio(), min = 0, max = 100, symbol = "%", gaugeSectors(
    danger = c(51, 100), warning = c(11, 50), succes = c(0, 10)
  ))
)
```

Row 
-----------------------------------------------------------------------

```{r}
renderPlot(
  ggplot(clean_custom_csv_data() %>%
           filter(nb_list_matched >= input$custom_nb_matched), aes(x = interest_lvl, fill = interest_lvl)) + geom_bar() + theme_bw() +
    theme(legend.position = "none") + ylab(NULL) + xlab("Niveau d'intérêt")
)
```

Summary
==================================================

Column {.sidebar}
-----------------------------------------------------------------------

```{r}
br()
fileInput("mydatafull", "Please load some valide csv file", accept = "csv", multiple = TRUE)

custom_csv_data_full <- reactive({
    infile <- input$mydatafull
    if (is.null(infile)) {
      # User has not uploaded a file yet
      return(NULL)
    } else{
      #read_csv(infile$datapath[4])
      map(infile$datapath,~read_csv(.x))
    }
  })

```

```{r, eval=TRUE}
renderUI({
  val_full <- ifelse(is.null(custom_csv_data_full()), 1, map_int(custom_csv_data_full(), ~ncol(.x)) %>% max - 2)
  radioButtons("custom_nb_matched_full", label = "Select number of thesaurus to be matched", choiceValues = 1:val_full, choiceNames = paste("At least", 1:val_full, "thesaurus matched out of", val_full))
})
```


```{r, eval=TRUE}
clean_custom_csv_data_full <- reactive(map(custom_csv_data_full(), ~.x %>%
                                  mutate(nb_list_matched = rowSums(.[-c(1,2)]), total_list = ncol(.) - 2) %>%
  filter(interest_lvl >= 0) %>%
  mutate(interest_lvl = as.factor(interest_lvl)))
)
```

Row
-----------------------------------------------------------------------
### Articles retrieved mean

```{r}
mean_retrieved <- reactive(map_int(custom_csv_data_full(), ~nrow(.x)) %>%
                             mean %>%
                             floor)
renderValueBox(
  valueBox(mean_retrieved(), icon = "fa-comments")
)
```

### Matched articles mean

```{r, eval=TRUE}
mean_custom_matched_articles <- reactive(map(clean_custom_csv_data_full(), ~.x %>%
                             filter(nb_list_matched >= input$custom_nb_matched_full)))
#renderPrint(c(map_int(keep(mean_custom_matched_articles(), ~nrow(.x) > 0), ~nrow(.x)) %>%
 #             mean %>%
  #            floor, map_int(keep(mean_custom_matched_articles(), ~nrow(.x) > 0), ~nrow(.x))))
mean_matched <- reactive(map_int(keep(mean_custom_matched_articles(), ~nrow(.x) > 0), ~nrow(.x)) %>%
              mean %>%
              floor)
renderValueBox(
  valueBox(mean_matched(), icon = "fa-comments")
)
```

### Matched articles ratio mean

```{r, eval=TRUE}
mean_custom_matched_ratio <- reactive(round(100*mean_matched()/mean_retrieved()))
renderGauge(
  gauge(mean_custom_matched_ratio(), min = 0, max = 100, symbol = "%", gaugeSectors(
    succes = c(80, 100), warning = c(31, 79), danger = c(0, 30)
  ))
)
```

Row 
-----------------------------------------------------------------------
### Articles matched mean 

```{r, eval=TRUE}
mean_custom_articles_matched <- reactive(map(clean_custom_csv_data_full(), ~.x %>%
                             filter(nb_list_matched >= input$custom_nb_matched_full)))
mean_matched1 <- reactive(map_int(keep(mean_custom_matched_articles(), ~nrow(.x) > 0), ~nrow(.x)) %>%
              mean %>%
              floor)
renderValueBox(
  valueBox(mean_matched1(), icon = "fa-comments")
)
```

### Matched articles liked mean

```{r, eval=TRUE}
mean_custom_matched_articles_liked <- reactive(map(mean_custom_articles_matched(), ~.x %>%
                             filter(interest_lvl == 2)))
mean_matched_liked <- reactive(map_int(keep(mean_custom_matched_articles_liked(), ~nrow(.x) > 0), ~nrow(.x)) %>%
                                         mean %>%
                                         floor)
renderValueBox(
  valueBox(mean_matched_liked(), icon = "fa-comments", color = "info")
)
```

### Matched articles liked ratio mean

```{r, eval=TRUE}
mean_custom_matched_liked_ratio <- reactive(round(100*mean_matched_liked()/mean_matched1()))
renderGauge(
  gauge(mean_custom_matched_liked_ratio(), min = 0, max = 100, symbol = "%", gaugeSectors(
    success = c(51, 100), warning = c(11, 50), danger = c(0, 10)
  ))
)
```

Row 
-----------------------------------------------------------------------
### Articles liked mean

```{r, eval=TRUE}
mean_custom_articles_liked <- reactive(map(clean_custom_csv_data_full(), ~.x %>%
  filter(interest_lvl == 2)))
mean_liked <- reactive(map_int(keep(mean_custom_articles_liked(), ~nrow(.x) > 0),~nrow(.x)) %>%
                                 mean %>%
                                 floor)
renderValueBox(
  valueBox(mean_liked(), icon = "fa-comments", color = "info")
)
```

### Liked articles lost mean

```{r, eval=TRUE}
mean_custom_liked_article_lost <- reactive(map(mean_custom_articles_liked(), ~.x %>% 
                                                 filter(nb_list_matched < input$custom_nb_matched_full)))
mean_liked_lost <- reactive(map_int(keep(mean_custom_liked_article_lost(), ~nrow(.x) > 0), ~nrow(.x)) %>%
                              mean %>%
                              floor)
#renderPrint(map_int(mean_custom_liked_article_lost(), ~nrow(.x)))
renderValueBox(
  valueBox(ifelse(!is.na(mean_liked_lost()), mean_liked_lost(), 0), icon = "fa-comments", color = "info")
)
```

### Liked articles lost ratio 

```{r, eval=TRUE}
mean_custom_liked_lost_ratio <- reactive(round(100*mean_liked_lost()/mean_liked()))
renderGauge(
  gauge(ifelse(!is.na(mean_custom_liked_lost_ratio()), mean_custom_liked_lost_ratio(), 0), min = 0, max = 100, symbol = "%", gaugeSectors(
    danger = c(51, 100), warning = c(11, 50), succes = c(0, 10)
  ))
)
```

Row 
-----------------------------------------------------------------------

```{r, eval=FALSE}
renderPlot(
  ggplot(clean_custom_csv_data_full() %>%
           filter(nb_list_matched >= input$custom_nb_matched_full), aes(x = interest_lvl, fill = interest_lvl)) + geom_bar() + theme_bw() +
    theme(legend.position = "none") + ylab(NULL) + xlab("Niveau d'intérêt")
)
```